A catalog of wide binaries and comoving star pairs from \textsl{Gaia DR1} and low-resolution spectroscopy

### 2017-06-29 paper/comoving-followup.tex
microtype
first stab at abstract

\include{gitstuff}
\include{preamble}
\graphicspath{{figures/}}

@@

\begin{document}

\title{Co-moving stars in \textsl{Gaia DR1}:
       a catalog of genuine comoving star pairs from low-resolution
       spectroscopic follow-up}

@@

\begin{abstract}
% Context
Widely-separated, co-eval stars are [...] for studying the chemical homogeneity
of birth, calibrating stellar atmosphere models across a range of [..], and for
modeling the Galactic tidal field.
Previous work using Hipparcos + literature RVs -> a few hundred genuine pairs
out to 8 pc.
% Aims
Identified candidate pairs using the Tycho-Gaia Astrometric Solution catalog,
Gaia DR1.
Want to identify genuinely dynamically associated pairs for future
high-resolution follow-up
% Methods
Low-resolution spectrograph to measure relative radial velocities to identify
genuine pairs.
% Results
Of the XX pairs observed, we find YY ...
% Conclusions
Gaia DR2 -> how many do we expect?
\end{abstract}

@@

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 321 unique star pairs and $\approx 120$
calibration targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:TODO}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python,\footnote{Released along with the code used to
generate the figures in this document at
\url{https://github.com/adrn/GaiaPairsFollowup}.} described below.

@@

>>>>

\include{gitstuff}
\include{preamble}
\graphicspath{{figures/}}
\usepackage{microtype}

@@

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me

\title{A catalog of wide binaries and comoving star pairs from \textsl{Gaia DR1}
       and low-resolution spectroscopy}

@@

\begin{abstract}
% Context
Widely-separated, coeval stars are powerful tools for testing star-formation
model predictions, improving stellar atmosphere models, and measuring the
mass distribution of the Milky Way.
They vastly outnumber the Galactic open clusters, but are still expected to
share a common origin and chemistry.
The kinematic properties of bound wide binaries and their unbound complements
serve as potentiometers for the smooth tidal field and perturbation spectrum in
the Milky Way.
Thus far, a few hundred genuine comoving star pairs with separations as large
as $8~\pc$ have been discovered in the solar neighborhood.
% Aims
In previous work, we have identified $\sim 10,000$ candidate comoving star pairs
using only astrometric data from the Tycho-Gaia Astrometric Solution (TGAS)
catalog, a part of \gaia\ \DR{1}.
However, without radial velocity measurements for the vast majority of the
pairs, the contamination rate at large separations is expected to be
considerable.
% Methods
Here, we present results from our own radial-velocity survey of a sample of the
candidate pairs to validate wide-separation comoving star pairs.
% Results
Of the XX comoving pairs observed, we find YY ...
% Conclusions
Gaia DR2 -> how many do we expect?
\end{abstract}

@@

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 321 unique star pairs and $\approx 120$
calibration targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:TODO}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python, described below.

@@

- Stellar rotation of evolved-main sequence
- Full catalog should contain Shaya and Olling, cross-match to RV surveys
